Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
Updated

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

@@

\begin{figure}[t]
	\includegraphics[width=0.5\textwidth]{images/cart_pole_SVRPG_vs_GPOMDP}
	\caption{On-line performance over sampled trajectories of SVRPG vs G(PO)MDP in the Cart-pole task, with 90\% t-student confidence intervals. Results denoted with $\dagger$ are taken from \cite{duan2016benchmarking}.}
	\label{fig:cartpole}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=0.5\textwidth]{swimmer_self_normalized_SVRPG_vs_SVRPG}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs unbiased SVRPG in the Swimmer task, with 90\% confidence intervals.}
	\label{fig:swimmertwo}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=0.5\textwidth]{swimmer_self_normalized_SVRPG_vs_GPOMDP}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs G(PO)MDP in the Swimmer task, with 90\% confidence intervals}
	\label{fig:swimmerone}
\end{figure}

>>>>

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\graphicspath{ {images/} }
%\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

@@

\begin{figure*}[t]
    \begin{minipage}[b]{0.3\textwidth}
	\includegraphics[width=.95\textwidth]{images/cart_pole_SVRPG_vs_GPOMDP_tex.pdf}
	\caption{On-line performance over sampled trajectories of SVRPG vs G(PO)MDP in the Cart-pole task, with 90\% t-student confidence intervals. Results denoted with $\dagger$ are taken from \cite{duan2016benchmarking}.}
	\label{fig:cartpole}
    \end{minipage}
    \begin{minipage}[b]{0.3\textwidth}
	\includegraphics[width=0.95\textwidth]{swimmer_self_normalized_SVRPG_vs_SVRPG_tex.pdf}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs unbiased SVRPG in the Swimmer task, with 90\% confidence intervals.}
	\label{fig:swimmertwo}
    \end{minipage}
    \hfill
        \begin{minipage}[b]{.3\textwidth}
	\includegraphics[width=0.95\textwidth]{swimmer_self_normalized_SVRPG_vs_GPOMDP_tex.pdf}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs G(PO)MDP in the Swimmer task, with 90\% confidence intervals}
	\label{fig:swimmerone}
    \end{minipage}
\end{figure*}
